Automating Verification of MPC Security

### 2023-06-09 popl24/hyperprop.tex
checkpoint

\subsection{A Sound Hyperproperty for Passive Security}
\label{section-nimo}
The intuition that passive security means that the protocol releases
no more information than what is released by conditioning on the
public output and corrupt inputs suggests a
refinement of noninterference. That is, the set of low equivalent
initial memories \emph{that can produce the same output} should generate the
same distributions of adversarial views.
\begin{definition}[Noninterference Modulo Output]
  We say that a program  $\prog$ satisfies \emph{noninterference modulo output},
  written $\NIMO(\prog)$, iff for all $H$, $C$, and 
  $\store_1,\store_2 \in \mems(S)$ we have:
  \begin{eqnarray*}
    & \store_1 =_C \store_2 \wedge
     (\margd{(\condd{\progd(\prog)}{\store_1})}{\{ \outv \}} =
     \margd{(\condd{\progd(\prog)}{\store_2})}{\{ \outv \}}) \\
    & \implies \\
    & \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}
  \end{eqnarray*}
where $\iov(\prog) = (S,V)$.
\end{definition}

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is:
  $$
  \{ \store | \idealf(\store) = v \}
  $$
  We say that $\idealf$ is \emph{invertible} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is invertible, implies
passive security of a protocol.
\begin{theorem}
  Assume given invertible $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If program $\prog$ satisfies
  noninterference modulo output for all $H$ and $C$ with $|H| < |C|$,
  then $\prog$ is passive secure.
\end{theorem}

@@

\begin{lemma}
  Given $H$, $C$, and a program $\prog$ with $\iov(\prog) = (S,V)$ and
  output view $x \in V$
  $\prog$ satisfies noninterference modulo output iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{(S \cup \{x\})_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}

>>>>

\subsection{A Sound Hyperproperty for Passive Security}
\label{section-nimo}
The intuition that passive security means that the protocol releases
no more information than what is released by conditioning on the
public output and corrupt inputs suggests a
refinement of noninterference. That is, the set of low equivalent
initial memories \emph{that can produce the same output} should generate the
same distributions of adversarial views.
\begin{definition}[Noninterference Modulo Output]
  We say that a program  $\prog$ satisfies \emph{noninterference modulo output},
  written $\NIMO(\prog)$, iff for all $H$ and $C$ with $|C|\le|H|$ and 
  $\store_1,\store_2 \in \mems(S)$ we have:
  \begin{eqnarray*}
    & \store_1 =_C \store_2 \wedge
     (\margd{(\condd{\progd(\prog)}{\store_1})}{\{ \outv \}} =
     \margd{(\condd{\progd(\prog)}{\store_2})}{\{ \outv \}}) \\
    & \implies \\
    & \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}
  \end{eqnarray*}
where $\iov(\prog) = (S,V)$.
\end{definition}

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is:
  $$
  \{ \store\ |\ \idealf(\store) = v \}
  $$
  We say that $\idealf$ is \emph{invertible} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is invertible, implies
passive security of a protocol.
\begin{theorem}
  Assume given invertible $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\NIMO(\prog)$
  then $\prog$ is passive secure.
\end{theorem}

@@

As for noninterference, we can show that $\NIMO$ is equivalent
to saying that a given program does not change the probability
of honest secrets conditioned on corrupt secrets and views
(including the output view), as compared to conditioning on
just the corrupt secrets and input. In addition to providing
insights about $\NIMO$, this form is helpful for
verification techniques. 
\begin{lemma}
  Given $H$, $C$, and a program $\prog$ with $\iov(\prog) = (S,V)$ and
  output view $x \in V$
  $\prog$ satisfies noninterference modulo output iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{(S \cup \{x\})_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}
